Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/future_work.tex
Reworked ideas, fixed various comments

In \cref{sec:intro}, we discussed the four dimensions of extensibility
that our properties should exhibit: architectures, enforcement mechanisms,
features, and requirements. We have focused on extending our basic system
with advanced features; a logical next step is extending to other enforcement
mechanisms. In the following, we discuss how different existing mechanisms
might fit into our model.

\subsubsection{Software Techniques}

\paragraph{Stack Canaries and Shadow Stacks}
%
Canaries are special values inserted by the caller at certain points of the
stack and checked for corruption on return, for protection against
some classes of control-flow hijacking (i.e., overwriting the caller's
return address through a buffer overflow that would also overwrite the canary
detectably). A shadow stack is a mirror image of the control-relevant parts of the stack,
maintained by the program to attempt to detect attempts to hijack its control
flow and ``restrict the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}.
%
These are hardening techniques that increase the difficulty
of some control-flow attacks on the stack, but cannot provide absolute
guarantees on \(\wbcf\) under a normal attacker model.
Interestingly, these are also lazy enforcement mechanisms, in that
the attack may occur and be detected some time later, before taking the

\paragraph{Bounds Checking}
%
Under a bounds checking discipline, all the pointers in a program are extended
with some disjoint metadata, and these are combined to gate memory accesses,
usually with the objective of enforcing some form of \emph{memory
safety} \rb{(relate this to the basic high-level concepts and types of attacks
we want to consider: control flow, some integrity and confidentiality?)}.
%
Compared to stack canaries and shadow stacks, bounds checking is eminently
a \emph{high-level} technique, designed with a particular programming language
in mind and implemented through a \emph{secure compiler} \cite{} that performs
the necessary code transformations. Also unlike those techniques (which make few
assumptions on callee code), it offers little to no protection
against \emph{adversarial low-level} code that is not constrained to obey the
bounds checking discipline.

\paragraph{Split Stacks}
%
Code-pointer integrity seeks to prevent control-flow hijacking attacks by
splitting the program memory, including the stack, into a regular region and a
safe region; objects that require protection are placed in the latter and
all accesses to them protected by static or dynamic checks.
%
Like shadow stacks, bounds checking is a high-level technique designed to
protect code written in a high-level language, but it is designed to
offer protection under a stronger threat model that also considers the presence
of untrusted code. As with most other software-based methods, it purports to
protect exclusively the control-relevant parts of the stack, making no claims
about its data-relevant parts.

\subsubsection{Hardware Techniques}

In addition to the many software-based techniques developed to provide greater
degrees of protection to the stack, often incurring a significant performance penalty,
some proposals have turned to specialized hardware features to offset those
costs and attempt to offer greater levels of protection.

We focus in particular on two families of hardware mechanisms: capability machines
and tag-based reference monitors. Both types of system move beyond simply
offering hardware acceleration for software-based techniques, offering hardware
primitives for both memory and control-flow enforcement that can offer a degree
of protection even with minimal cooperation from the code.
%
\rb{Something about how realistic/practical these alternatives are? Are we
  selecting partly based on prototypes, etc.?}

\paragraph{Capabilities}
%
\rb{(There is plenty of variety here, should we focus on the Cerise-and-friends
  (CHERI-adjacent) work exclusively?)}

\sna{If we have good examples of other capability systems, we should absolutely
  talk about them. No need to privilege CHERI.}
%
Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has uses these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.
%
They are closely related \rb{too strong?} to this work; we discuss them in more
detail in \cref{XXX}.
%

\paragraph{Micro-Policies}
%
\rb{(This partly overlaps with the technical preliminaries, try to offer a quick
  synthesis here.)}
%
Micro-policy machines are a family of tagged architectures that decorate
addressable memory and registers with arbitrary metadata tags, and extend the
processor with a programmable hardware monitor that uses custom rules on
metadata tags to implement many different kinds of security policies.
%
This flexibility can be harnessed to implement a wide array of stack protection policies with relative ease, covering and going beyond the capabilities \rb{word choice?} of the various software-based techniques \cite{} \rb{as demonstrated by}.
%
These policies comprise very general forms of \emph{lazy enforcement}, which can tolerate
potential but harmless violations \rb{the system programmer's motto: ``trust me,
  I know what I'm doing''} while still detecting them if and when their effects
become observable. 
%
Micro-policies are one of the centerpieces of our technical development; we
present them in more detail in \cref{XXX}.

\paragraph{Summary}

We begin to see that the security of the call stack and its contents is not
clearly defined. Different protection mechanisms aim to protect the stack
in fundamentally different ways, each offering a \emph{unique}, \emph{implicit}
specification of the meaning of ``stack safety.'' These specifications
may be more or less compatible with the needs of a given high-level language.
Moreover, different protections operate under different threat models, further
complicating their comparison and the assessment of the safeguards they
effectively offer their clients---the programs themselves.
It would be far preferable to have a \emph{standard}, \emph{explicit} specification.
Only a handful of works have offered any explicit specification.

>>>>

In \cref{sec:intro}, we discussed several dimensions of flexibility
that our properties should exhibit: applicability to different system
features and different security requirements. Another important dimension
is applicability to multiple enforcement mechanisms.
In the following, we discuss how different existing mechanisms
might fit into our model.

\paragraph{Stack Canaries and Shadow Stacks}
%
Canaries are special values inserted by the caller at certain points of the
stack and checked for corruption on return, for protection against
some classes of control-flow hijacking (i.e., overwriting the caller's
return address through a buffer overflow that would also overwrite the canary
detectably). A shadow stack is a mirror image of the control-relevant parts of the stack,
maintained by the program to attempt to detect attempts to hijack its control
flow and ``restrict the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}.
%
Interestingly, these are lazy enforcement mechanisms, in that
the attack may occur and be detected some time later, as long as
it is detected before it can become dangerous. That would make our
formalism a good fit for defining their security, except that
they are chiefly hardening techniques: they increase the difficulty
of some control-flow attacks on the stack, but cannot provide absolute
guarantees on \(\wbcf\) under a normal attacker model.

\paragraph{Split Stacks}
%
Code-pointer integrity seeks to prevent control-flow hijacking attacks by
splitting the program memory, including the stack, into a regular region and a
safe region; objects that require protection are placed in the latter and
all accesses to them protected by static or dynamic checks.
%
Like shadow stacks, bounds checking is a high-level technique designed to
protect code written in a high-level language, but it is designed to
offer protection under a stronger threat model that also considers the presence
of untrusted code. As with most other software-based methods, it purports to
protect exclusively the control-relevant parts of the stack, making no claims
about its data-relevant parts---we would solely be testing \(\wbcf\).

\paragraph{Bounds Checking}
%
Under a bounds checking discipline such as Softbound \cite{}, all the pointers
in a program are extended with some disjoint metadata, and these are combined
to gate memory accesses. These approaches enforce a form of \emph{memory safety},
and we would therefore expect them to enforce \(\clri\) and \(\clrc\). They aim
to enforce \(\wbcf\) by cutting off attacks that involve memory-safety violations,
but that may not be sufficient.

Bounds checking approaches require substantial compiler cooperation. This is not a
problem for our properties in general, but it is not very compatible with
generation-by-execution of low-level code. A better choice would be to generate
high-level code using a tool like CSmith \cite{}, or prove the properties instead.

\paragraph{Capabilities}

Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has uses these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.

There are several proposals around the use of Cheri capabilities to enforce stack safety,
including mechanisms that use the standard Cheri hardware (which includes local
capabilities) \cite{SkorstengaardLocal},
and others that propose entirely new types of capabilities, such as linear
\cite{SkorstengaardSTK}, uninitialized \cite{Georges+21}, lifetime
\cite{Tsampas+19}, and directed \cite{Georges22:TempsDesCerises} capabilities.
It is a high priority to test this most recent work by Georges et al., as it is designed
to be similar to all of our properties except for \(\clei\).

\subsection{More Features}

Several common features did not make it into this work: most importantly concurrency and
exceptions. We plan to extend the model to include them, and then test them. We would also
like to test the model given in \cref{app:ptr} for arbitrary memory-safe pointer sharing.

### 2023-02-02 submission5/ideas-v1.tex
Reworked ideas, fixed various comments

The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. Then in \cref{sec:machine} we will introduce the machine model that we test, and give
its {\em security semantics}, described in brief below. We formalize the definitions of
stack safety that derive from the security semantics in \cref{sec:props}.
\Cref{sec:testing} describes the testing framework, and
\cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.

@@

@@

\paragraph*{Threat Model}

We must trust that our method of distinguishing security-relevant operations is accurate; if it
involves labels placed on code by a compiler, that means trusting that the compiler placed
those labels correctly. If operations occur that are not recognized, those operations
might not be guaranteed to protect their principals---for instance, an unlabeled call
might not protect the caller's data from the callee. On the flip side, applying an incorrect
label most likely means that the property becomes too strong to be enforced.

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers are treated appropriately by whichever compiler
generated their code. Our properties explicitly require them to be treated as belonging
to the caller, which could be enforced by a micro-policy or by a well-behaved compiler.

In general, it is impossible to distinguish buggy machine code from an attacker; in
our examples we will identify one function or another as an attacker, but we do not
require any static division between trusted and untrusted code, and we aim to protect
even buggy code.

This is a strong threat model, but it does omit some important aspects of
security enforcement: In particular, hardware and timing attacks are out of scope.

>>>>

The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. In the process we discuss some motivation for the properties, from a security
perspective: we consider a simple attacker, and discuss the harm that it can do to
its caller. This perspective is essential to understanding how lazy enforcement can
be safe: even if an attacker can overwrite some memory, if it cannot accomplish
its bigger-picture goals, the system is safe.

Then in \cref{sec:machine} we will introduce the machine model that we test, and give
its {\em security semantics}, described in brief below. We formalize the definitions of
stack safety that derive from the security semantics in \cref{sec:props}.
\Cref{sec:testing} describes the testing framework, and
\cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.

@@

Whatever the mechanism for labeling transitions, we get a base
machine transition \(\mach \xrightarrow{\bar{\psi}, \obs} \mach'\), where \(\obs\) is
an event (see below) and \(\bar{\psi}\) is a list of security-relevant operations.
We then lift this into a transition between pairs of machine states and contexts,
\((\mach,\context) \stepstounder{\overline{\psi},\obs} (\mach', \context')\).

@@

\paragraph*{Variants and Non-interference}

To characterize confidentiality, we borrow the idea of \emph{variant} states
from the theory of non-interference. Non-interference is a way of expressing
the flow of information through the system. If we begin with a state \(\mach\)
and modify it to \(\nach = \mach[\component \mapsto v]\) for arbitrary \(v\),
then execute both \(\mach\) and \(\nach\), any differences in the outputs they
produce must be the result of accessing \(\component\).

\paragraph*{Putting It Together}

Putting these ideas together, we get the basic structure of a property in our model.
First we define the security-relevant operations that we support, a security context,
and the function according to which the security context updates with each step.
Then, we define a predicate on states and contexts that expresses the requirements
for our security property, using variants, assertions about future states, and comparison
of event traces. Finally, in order to apply the property to a specific machine, we
must determine how the machine's execution translates into security relevant operations.

### 2023-02-02 submission5/intro-v2.tex
Reworked ideas, fixed various comments

Of these mechanisms, many are fundamentally ill-suited for offering formal guarantees,
as they aim to impede attackers but cannot provide universal protection. Stack canaries,
for instance, aim to reduce the ability of attackers to find gadgets, not to categorically
rule out attacks. Others may be amenable to formalization but do not offer it.
The Cerise work of Skorstengaard et al. \cite{SkorstengaardSTKJFP} and
Georges et al. \cite{Georges22:TempsDesCerises} is so far the sole line of work
to offer (various) stack safety formalizations.

Meanwhile, Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies for stack safety, at least some of which should be amenable to making
formal guarantees. Among these is their ``Lazy Tagging and Clearing'' \(LTC\) micropolicy,
which is is peculiar in that function activations may write into one another's stack frames,
as long as the data cannot be accessed afterward. As a result, \(LTC\) definitely would not
fulfill a tag-based adaptation Georges et al.'s state-of-the-art property.
\rb{(Do we explain why anywhere?)}
Roessler and DeHon themselves do not claim that it intends to enforce stack safety,
only an approximation.

We disagree. \(LTC\) does not always protect individual addresses on the stack, but it aims
to prevent one function activation from interfering with another's behavior---to protect
the functional abstraction. We argue that a formal characterization of \(LTC\)'s protections
should fall under the umbrella of stack safety.

@@

%Security mechanisms can be brittle, successfully eliminating one attack while leaving room for
%other, similar attacks. To avoid this, we seek formal properties of safe behavior that can be proven
%or tested. Such properties become the specification against which enforcement can be validated;
%even enforcement mechanisms that do not fulfill a property benefit from the ability to articulate
%\emph{why} they fail.

Most security properties are described at the level of a high-level programming language,
and translated to the target-level via a secure compiler. Stack safety cannot
be defined in this way, as the abstraction is completely transparent in most source languages.
(Contrast Azevedo de Amorim et al.'s \cite{DBLP:conf/post/AmorimHP18} work on heap safety,
which is broadly consistent across language semantics, and therefore
amenable to a very general high-level approach.)
But it is not satisfying as a low-level property; at the level of the ABI, the
specification of a well-behaved stack is minimal. It is not concerned with such
questions as whether a caller's frame should be readable or writable to its callee,
leaving those concerns to be determined by a high-level language built atop the stack.

@@

These two cases represent two dimensions of generality that make stack safety difficult to
define as a single, universal property: what constitutes safe behavior may differ between
systems that support different features, and different types of security may be more or less
desirable depending on context.

We are not attempting to present a universal definition of stack safety for all systems.
Rather, we define the stack safety of a single, fairly realistic system (one with common
features such as memory arguments and tailcall elimination), decomposed into
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for integrity, confidentiality, and control flow
to obey the requirements. This decomposition can be thought of as a step toward
a universal definition, in that the definitions in (3) capture fundamental
notions of security that can then be applied flexibly to other systems by varying
the model in (1) and (2).

To address the second class of generality, we present a total of five core properties:
\(\wbcf\), caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)). These are defined
formally in \cref{sec:props}. They are related to one another as seen in
\cref{fig:propertydiagram}: \(\clei\) subsumes \(\clrc\) and \(\clec\) subsumes
\(\clri\), but otherwise the properties are orthogonal. We further define two
important combinations of properties: full stack safety \(\textnormal{\sc FSS}\),
and caller safety \(\textnormal{\sc ClrS}\). Of these, most existing concepts of
stack safety correspond to either \(\wbcf\) or \(\textnormal{\sc ClrS}\), which are
concerned with the basic guarantees that the caller recieves during the call, while
\(\textnormal{\sc FSS}\) is a natural extension that enforces a higher-level concept
of a correct interface between caller and callee. \sna{Blah. Needs work.}

To validate our formal characterization, we use these
properties to test and improve an existing enforcement mechanism, the
{\em stack safety micro-policies} of Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}, re-implemented
in the Coq proof assistant on top of a \rb{formal} RISC-V specification.  We
use QuickChick~\cite{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for Coq, to generate random programs and check
that Roessler and DeHon's micro-policies correctly detect the ones that
attempt to violate one of our properties. Furthermore, we
check that the testing framework is able to generate counterexamples
that violate our properties but are \emph{not} halted by incorrect
variants of the enforcement mechanisms, including ones that we accidentally created
while implementating the micro-policy and ones that we
intentionally crafted to increase our confidence in the effectiveness
of our testing.
%
\rb{This and the following paragraph could start more generally (we need to
  answer the question of why these experiments, what is their interest), and
  probably motivate the use of PBT (experiment results below show there's
  benefit in them!) and, somewhere at least, talk about other points in the
  spectrum.}

We find that Roessler and DeHon's \emph{Lazy Tagging and Clearing}
violates the temporal aspect of confidentiality in
cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak uses the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that testably enforces
confidentiality, albeit at some performance cost.
%
\rb{Anything to add from personal communications? More details later? Shows
  these things are very hard to get right -- like the latest work on Cerise,
  also motivated by this very work.
\rb{(+SNA) At the very least, these models are subtle and getting them right,
  and describing them unambiguously, is hard without a framework like this.}
}

@@

\begin{itemize}
\item We formalize permissive stack confidentiality and integrity properties,
  which are parameterized over a notion of external
  observation, and are violated only if accessing secrets or overwriting
  data causes a visible change in system behavior.
\item We instantiate these definitions with a realistic
  system with features such as argument passing
  on the stack, callee-saves registers, and tail-call elimination.
  Our model is modular enough that adding these features is straightforward.
\item Our formalization of well-bracketed control flow in the presence of tail-call
  elimination \ifexceptions and exceptions \fi is a novelty over existing models.
\item We use property-based random testing to validate the relationship between
  our properties and micro-policies.
\end{itemize}

@@

>>>>

Of these mechanisms, many are fundamentally ill-suited for offering formal guarantees,
as they aim to impede attackers but cannot provide universal protection. Shadow stacks,
for instance, aim to ``restrict the flexibility available in creating gadget chains''
\cite{Shanbhogue+19} not to categorically
rule out attacks. Other mechanisms are stronger, but relatively few formally state their guarantees.
The Cerise work of Skorstengaard et al. \cite{SkorstengaardSTKJFP} and
Georges et al. \cite{Georges22:TempsDesCerises} is so far the sole line of work
to offer (various) stack safety formalizations.

Meanwhile, Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies for stack safety, at least some of which should be amenable to making
formal guarantees. Among these is their ``Lazy Tagging and Clearing'' \(LTC\) micropolicy,
which is is peculiar in that function activations may write into one another's stack frames,
as long as the data cannot be accessed afterward. As a result, \(LTC\) definitely would not
fulfill a tag-based adaptation Georges et al.'s state-of-the-art property.

We believe that, nevertheless, \(LTC\) enforces stack safety.
It does not always protect individual addresses on the stack, but it aims
to prevent one function activation from interfering with another's behavior---to protect
the functional abstraction. We argue that a formal characterization of \(LTC\)'s protections
should fall under the umbrella of stack safety.

@@

Security mechanisms can be brittle, successfully eliminating one attack while leaving room for
other, similar attacks. To avoid this, we seek formal properties of safe behavior that can be proven
or tested. Such properties become the specification against which enforcement can be validated;
even enforcement mechanisms that do not fulfill a property benefit from the ability to articulate
\emph{why} they fail.

We take the view that security properties should be motivated by security requirements,
and flexible enough to support various sets of security requirements depending on the
goals of the system that they validate.
Following this reasoning, our vision of stack safety is as a collection of properties
describing the security needs of a system with regard to its functional abstractions.
While the stack still plays a key role, our stack safety is about functions. The most
dramatic consequence of this is that we treat registers as part of a function activation's
state, and hold them to the same protection requirements as stack memory.

Flexibility is especially important for stack safety.
%
Most security properties are described at the level of a high-level programming language,
and translated to the target-level via a secure compiler. Stack safety cannot
be defined in this way, as the abstraction is completely transparent in most source languages.
(Contrast Azevedo de Amorim et al.'s \cite{DBLP:conf/post/AmorimHP18} work on heap safety,
which is broadly consistent across language semantics, and therefore
amenable to a very general high-level approach.)
%
But it is not satisfying as a low-level property; at the level of the ABI, the
specification of a well-behaved stack is minimal. The ABI is not concerned with such
questions as whether a caller's frame should be readable or writable to its callee,
leaving those concerns to be determined by a high-level language built atop the stack.
These are high-level security questions.

@@

These two cases represent two dimensions in which a stack safety definition requires
flexibility: what constitutes safe behavior differs between systems that support different
features, and different contexts have different top-level security requirements.

We are not attempting to present a universal definition of stack safety for all systems,
but we do construct our definition with these dimensions of flexibility in mind.
Our model is decomposed into:
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for the integrity, confidentiality, and control flow
requirements.

We show that we can extend our system to new features by first introducing a simple
example model, and then moving to a more realistic model with multiple new features:
callee-save registers, argument passing on the stack, and tailcall elimination, simply
by refining a few definitions in (1). This becomes the model that we validate.
In \cref{???}, we extend the model further with arbitrary sharing of memory-safe
pointers. Our criteria in (3) cover a total of five core requirements:
\(\wbcf\), caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)).
They are related to one another as seen in
\cref{fig:propertydiagram}: \(\clei\) subsumes \(\clrc\) and \(\clec\) subsumes
\(\clri\), but otherwise the properties are orthogonal and can be taken piecemeal
according to the needs of a system.

In particular, many enforcement techniques focus purely on
well-bracketed control flow. Stack canaries aim to prevent certain attacks on the return
address, and shadow stacks with protection (e.g. Return Address Defender \cite{Chiueh2001RAD})
to enforce it completely. Others combine this protection with some degree of memory protection,
chiefly focusing on integrity. Interestingly, Skorstengaard et al. \cite{SkorstengaardSTKJFP}
describe their ``local state encapsulation'' in terms of integrity, but it is equivalent
to the combination of \(\clri\) and \(\clrc\). It is not until Georges et al. \cite{Georges22:TempsDesCerises}
that the Cerise line of work considers confidentiality; they also consider \(\clec\), but not
\(\clei\). \sna{It is really tempting to find a way to take credit for this.}

%These are defined
%formally in \cref{sec:props}. . We further define two
%important combinations of properties: full stack safety \(\textnormal{\sc FSS}\),
%and caller safety \(\textnormal{\sc ClrS}\). Of these, most existing concepts of
%stack safety correspond to either \(\wbcf\) or \(\textnormal{\sc ClrS}\), which are
%concerned with the basic guarantees that the caller recieves during the call, while
%\(\textnormal{\sc FSS}\) is a natural extension that enforces a higher-level concept
%of a correct interface between caller and callee. \sna{Blah. Needs work.}

Flexibility aside, we show that our properties are useful for their purpose:
distinguishing correct enforcement from incorrect. We use
QuickChick~\cite{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for Coq, to generate random programs and check that the
stack safety {\em micro-policies} of Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}
correctly detect the ones that attempt to violate one of our properties. Furthermore, we
check that the testing framework is able to generate counterexamples
that violate our properties but are \emph{not} halted by incorrect
variants of the enforcement mechanisms---including the original \(LTC\)!

@@

\begin{itemize}
\item A novel characterization of stack safety as a collection of properties:
  confidentiality and integrity for callee and caller, and well-bracketed
  control-flow. These can characterize the security requirements of systems
  that support only some portion of stack safety, and are
  parameterized over a notion of external observation, so that they can characterize
  lazy enforcement.
\item An instantiation of these definitions in a realistic
  setting with features such as argument passing
  on the stack, callee-saves registers, and tail-call elimination.
  Our model is modular enough that adding these features is straightforward.
\item The validation, via property-based randomize testing, of tag-based
  stack-safety policies. We find that \emph{Lazy Tagging and Clearing}
  falls short of stack safety, and propose a fix.
\end{itemize}

@@

\subsection{Threat Model and Limitations}

When our properties are used to evaluate a system, the threat model will depend on the
details of that system. However, there are some constraints that our design puts on
any system. We must trust that the method of distinguishing security-relevant operations is accurate; if it
involves labels placed on code by a compiler, that means trusting that the compiler placed
those labels correctly. If operations occur that are not recognized, those operations
might not be guaranteed to protect their principals---for instance, an unlabeled call
might not protect the caller's data from the callee. On the flip side, applying an incorrect
label most likely means that the property becomes too strong to be enforced.

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers are treated appropriately by whichever compiler
generated their code. Our properties explicitly require them to be treated as belonging
to the caller, which could be enforced by a micro-policy or by a well-behaved compiler.

In general, it is impossible to distinguish buggy machine code from an attacker; in
our examples we will identify one function or another as an attacker, but we do not
require any static division between trusted and untrusted code, and we aim to protect
even buggy code.

This is a strong threat model, but it does omit some important aspects of
security enforcement: in particular, hardware and timing attacks are out of scope, and
we do not address concurrency.
